---
title: "NUSmodAn"
author: "Aaron0696"
output:
  github_document:
    toc: true
    toc_depth: 3
    fig_width: 4
    fig_height: 4
  html_document:
    fig_align: center
    code_folding: show
    number_sections: true
    highlight: haddock
    theme: yeti
    toc: yes
    toc_float: yes
    df_print: paged
---

# Phase 1: Setting Up Environment, Packages And Loading Data.

## >Packages And Options

* Load packages.

```{r setup, warning = FALSE, message = FALSE}
# rmarkdown::render(input = "NUSmodAn.Rmd",
#                   output_format = "github_document",
#                   output_file = "README.md")
library(semTools)
library(ggplot2)
library(rjson)
library(stringr)
library(DT)
library(psych)
library(corrplot)
library(dplyr)
options(width = 999)
knitr::opts_chunk$set(dpi = 300)
knitr::opts_chunk$set(out.width = "50%")
```

## >>Bidding Data From `nusmods`

* Extract data from `nusmods` API at https://nusmods.com/api/.
* CORS bidding data.

```{r extract, eval=FALSE}
# load bidding data
# calculate loading times
before <- Sys.time()
# read data directly from URL
myjson <- fromJSON(file = url("https://api.nusmods.com/corsBiddingStatsRaw.json"))
# create empty dataframe which will act as a container to be populated with data
myBid <- data.frame()
# for each element in the myjson list, append it to myBid
for(r in 1:length(myjson))
{
  if(myjson[[r]]$Semester == 1 | myjson[[r]]$Semester == 2)
  {
    myBid <- rbind(myBid, myjson[[r]])
  }
  myjson[[r]] <- NA
}
# calculate loading time
after <- Sys.time()
after - before
# remove myjson to free up some RAM
rm(myjson)
# peek at the data
head(myBid)
tail(myBid)
# data struct
str(myBid)
# save
saveRDS(myBid, file = "myBid.RDS")
```

## >>Load `myBid.RDS`

```{r loadrds}
myBid <- readRDS("mydata.RDS")
```    

## >Module Information

```{r extract2, eval=FALSE}
myjson <- fromJSON(file = url("https://nusmods.com/api/moduleTimetableDeltaRaw.json"))
# create empty dataframe which will act as a container to be populated with data
myModInfo <- data.frame()
# for each element in the myjson list, append it to myBid
for(r in 1:length(myjson))
{
  if(myjson[[r]]$Semester == 1 | myjson[[r]]$Semester == 2)
  {
    myModInfo <- rbind(myModInfo, myjson[[r]])
  }
  myjson[[r]] <- NA
}

# save
saveRDS(myModInfo, file = "myModInfo.RDS")
```

## >>Load `myModInfo.RDS`

```{r loadrds2}
myModInfo <- readRDS("myModInfo.RDS")
```

# Phase 2: Filter, Transform And Merge Data
    
## >`myModInfo`

* Filter Module Information, `myModInfo`.
    * Removing non-Psychology modules.
    * Removing tutorial information.
    * Removing duplicated rows.

### >>Filter

```{r filter1}
# only keep the Psychology modules information
myModInfo <- subset(myModInfo,
                     str_detect(myModInfo$ModuleCode, "^PL"))
```

```{r filter1.1}
# remove information about tutorials
myModInfo <- subset(myModInfo,
                    myModInfo$LessonType != "TUTORIAL")
```

```{r filter1.2}
# only keep these columns
myModInfo <- myModInfo[,grep("ModuleCode|DayText|StartTime|Semester|AcadYear", names(myModInfo))]
# remove duplicated rows based on columns of ModuleCode, Acadyear and Semester
myModInfo <- distinct(myModInfo, 
                      ModuleCode, AcadYear, Semester, StartTime, DayText)
```  
    
## >`myBid`

* Filter CORS Bidding Information, `myBid`.
    * Removing non-Psychology modules, including Roots and Wings (PLS) and Psychology for non-Psychology students (PLB).
    * Removing information from reserved modules.

### >>Filter

```{r filter2}
# remove non-psychology modules
myBid <- subset(myBid,
                 # only keep rows where module code begins with PL
                 str_detect(myBid$ModuleCode, "^PL"))

# also remove Roots and Wings (PLS8001) and psychology for non-psych students (PLB1201)
myBid <- subset(myBid,
                 !str_detect(myBid$ModuleCode, "PLS|PLB"))

# remove the rounds where it was reserved
myBid <- subset(myBid,
                     !str_detect(myBid$StudentAcctType, "Reserved"))

# remove unneeded columns
myBid <- myBid[, -grep("Group|Faculty", names(myBid))]
```

## >>Transform And Merge

* Transform
    * Created a new variable `Level` that denotes whether the module is Level 1, 2, 3 or 4.
    * Created a new variable `BpQ` that represents Bids per Quota, which is the number of bidders for each available quota of the module, derived from `Bidders` and `Quota`. Used as a measure of the popularity of a module, Higher `BpQ` signifies greater popularity.
    * Created a new variable `LessonTime` that denotes whether the lecture begins in the morning (before 12pm), in the afternoon (12pm to 4pm), in the evening (after 4pm).
* Merge
    * Add the information from `myModInfo` to `myBid`.

```{r transform1}
# create new column that indicates the level of the module, based on their module code
myBid$Level <- ifelse(str_detect(myBid$ModuleCode, "1[0-9][0-9][0-9]"), "Level 1",
                       ifelse(str_detect(myBid$ModuleCode, "2[0-9][0-9][0-9]"), "Level 2",
                              ifelse(str_detect(myBid$ModuleCode, "3[0-9][0-9][0-9]"), "Level 3",
                                     ifelse(str_detect(myBid$ModuleCode, "4[0-9][0-9][0-9]"), "Level 4", 
                                            "Graduate Module"))))
# crosstabs to doublecheck
# xtabs( ~ ModuleCode + Level, 
#        data = myBid, subset = NULL)
```

```{r transform1.1}
# create new column Bids Per Quota (BpQ)
myBid$BpQ <- as.numeric(myBid$Bidders)/as.numeric(myBid$Quota)
```

```{r transform1.2}
# create new column Bids Per Quota (BpQ)
myModInfo$LessonTime <- ifelse(as.numeric(myModInfo$StartTime) < 1200, "Morning",
                            ifelse(as.numeric(myModInfo$StartTime) > 1600, "Evening",
                                   "Afternoon"))
```

```{r merge}
# note: there is only module information from AY2016/17 onwards
# all data before that period will be dropped
mydata <- merge(x = myBid, 
                 y = myModInfo,
                 by = c("ModuleCode", "AcadYear", "Semester"))
```

## >Coercing Columns To Factors/Numeric

```{r transform2}
# transform these columns to numeric
for(r in c("Quota", "Bidders", "LowestBid", "LowestSuccessfulBid", "HighestBid", "StartTime"))
{
  mydata[,grep(r, names(mydata))] <- as.numeric(mydata[,grep(r, names(mydata))])
}
# transform these columns to factors
for(r in c("AcadYear", "Semester", "ModuleCode", "Round", "Level", "StudentAcctType", "DayText", "LessonTime"))
{
  mydata[,grep(r, names(mydata))] <- factor(mydata[,grep(r, names(mydata))])
}
```

## >Vectors Of Column Names

```{r colvecs}
# create vector of the column names which are factors
facnames <- names(select_if(mydata, is.factor))
# factor names without ModuleCode and StudentAcctType
facnames.mod <- facnames[-grep("ModuleCode|StudentAcctType", facnames)]
# create vector of the column names which are numeric
numnames <- names(select_if(mydata, is.numeric))
# numeric names without StartTime
numnames.time <- names(select_if(mydata, is.numeric))[-grep("StartTime", numnames)]
```

## >Rearranging `DayText` Levels

```{r daytext}
mydata$DayText <- factor(mydata$DayText,
                         levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday"))
```

## >Rearranging `LessonTime` Levels

```{r lessontime}
mydata$LessonTime <- factor(mydata$LessonTime,
                         levels = c("Morning", "Afternoon", "Evening"))
```

# Phase 3: Data Diagnostics

* Plot univariate histograms and bivariate plots using loops for **almost every** combination of variables.
* The graphs from this section are predominantly for diagnostics rather than exploration, what I mean is that the graphs from this section would make little sense if one tried to draw insights from them. This is because they are aggregated across all other variables.
    * For example: The mean of `Bidders` is calculated across all academic years, all bidding rounds, all modules...
* What I am looking out for in this section are odd patterns, like zeroes in places where they shouldn't be, missing data, highly non-normal data, variables with outliers, etc...
* Some observations and thoughts
    * The bidding statistics are highly non-normal, likely due to being bounded by zero (they cannot bid negative points or have negative bidders). May consider using zero-inflated or poisson regression if considering these statistics as dependent variables.
    
## Univariate Descriptive Statistics

```{r unides}
describe(mydata)
```

```{r unisum}
summary(mydata)
```

## Univariate Histograms

```{r explore1, warning = FALSE, eval = TRUE}
# plot the categorical variables
# note: I did not include ModuleCode in this exploratory graph because it has too many levels (83)
for(r in facnames.mod)
{
  cat(paste0("Histogram Of ", r))
  
  plot(
    ggplot(data = mydata, aes_string(x = r, fill = r)) + 
  geom_histogram(stat = "count") + 
  ylab("Count") +
  ggtitle(paste0("Count of ", r)) +
  theme_classic() + 
  theme(axis.text.x = element_text(angle = 90, size = 6, vjust = -0.3),
        axis.title.x = element_blank())
  )
}
```

```{r explore2, warning = FALSE, eval = TRUE}
# plot the continuous variables
for(r in numnames)
{
  cat(paste0("Histogram Of ", r))
  
  plot(
    ggplot(data = mydata, aes_string(x = r, fill = r)) + 
  geom_histogram(bins = 90, fill = "violetred") + 
  ylab("Histogram") +
  ggtitle(paste0("Frequency of ", r)) +
  theme_classic() + 
  theme(axis.text.x = element_text(angle = 90, size = 6, vjust = -0.3),
        axis.title.x = element_text())
  )
}
```

## Bivariate Plots

### Categorical-Categorical

```{r explorecatcat, warning = FALSE, eval = TRUE}
# create vector to loop across
for(r in 1:length(facnames.mod))
{
  for(i in 1:length(facnames.mod))
  {
   # dont do anything if they are the same or the graph has been made before
   if(i == r | i < r)
   {
   } else {
     cat(paste0(facnames.mod[r]," ~ ",facnames.mod[i]))
     
     # create formula for xtabs
     tempform <- paste0("~ ", facnames.mod[r], " + ", facnames.mod[i])
     # temp is a dataframe that is only going to exist in this section
     # and overwritten with each loop
     temp <- as.data.frame(xtabs(eval(parse(text = tempform)),
                            data = mydata,
                            subset = NULL))
     plot(
       ggplot(data = temp, aes_string(x = facnames.mod[r], y = facnames.mod[i], fill = "Freq", label = "Freq")) +
         geom_tile() + 
         geom_text() + 
         scale_fill_gradient(low = "white", high = "violetred") + 
         theme_minimal() + 
         theme(axis.text.x = element_text(angle = 90, vjust = -0.3))
     )
   }
  }
}
```

### Continuous-Continuous

```{r exploreconcon, warning = FALSE, eval = TRUE}
for(r in 1:length(numnames))
{
  for(i in 1:length(numnames))
  {
   # dont do anything if they are the same or the graph has been made before
   if(i == r | i < r)
   {
   } else {
     cat(paste0(numnames[r]," ~ ",numnames[i]))
     # create formula for lm()
     tempform.std <- paste0("scale(", numnames[i],")", " ~ ", "scale(", numnames[r], ")")
     tempform <- paste0(numnames[i], " ~ ", numnames[r])
     # regress to get best fit line
     # standardized
     stdreg <- lm(eval(parse(text = tempform.std)),
               data = mydata)
     # unstandardized
     reg <- lm(eval(parse(text = tempform)),
               data = mydata)
     
     plot(
       ggplot(data = mydata, aes_string(x = numnames[r], y = numnames[i])) +
         geom_point(color = "violetred", size = 2, alpha = 0.3) +
         theme_classic() + 
         geom_abline(slope = reg$coefficients[2], intercept = reg$coefficients[1], lty = "dashed") + 
         geom_label(aes(x = Inf, y = Inf, label = paste0("Standardized Regression Coefficient = ",
                                                         round(stdreg$coefficients[2],3)),
                        hjust = 1, vjust = 1)) + 
         theme(axis.text.x = element_text(angle = 90, vjust = -0.3))
     )
   }
  }
}


```

### Correlation Matrix

```{r corrmatrix, fig.width = 4, fig.height = 4}
corrplot.mixed(cor(mydata[,grep(paste0(numnames.time, collapse = "|"), names(mydata))]),
               upper = "color",
               tl.pos = "lt",
               tl.cex = 0.5,
               cl.cex = 0.5)
```

### Continuous-Categorical

```{r exploreconcat, warning = FALSE, eval = TRUE}
for(r in facnames.mod)
{
  for(i in numnames)
  {
    cat(paste0(r," ~ ",i))
    # graph
    plot(
      ggplot(data = mydata, aes_string(x = r, y = i, fill = r)) + 
      geom_bar(stat = "identity") + 
      theme_classic() + 
      theme(legend.position = "none",
            axis.text.x = element_text(angle = 90, vjust = -0.3))
    )
  }
}
```

### By Module

```{r exploremodule, fig.height = 12, warning = FALSE, eval = TRUE}
for(i in numnames)
{
  cat(paste0("ModuleCode"," ~ ",i))
  # graph
  plot(
    ggplot(data = mydata, aes_string(x = "ModuleCode", y = i, fill = "ModuleCode")) + 
      geom_bar(stat = "identity") + 
      theme_classic() + 
      theme(legend.position = "none",
            axis.text.x = element_text(angle = 90, vjust = -1)) + 
      coord_flip()
  )
}
```

# Phase 5: Exploration

```{r numods}
# number of modules
unique(mydata$ModuleCode)
```

```{r rowsmod}
# number of rows belonging to each module
xtabs(~ ModuleCode, data  = mydata, subset = NULL)
```

```{r}
# datatable(mydata)
aggregate(BpQ ~ AcadYear + Semester + ModuleCode,
          data = mydata,
          FUN = mean)
```




